Significance testing with forward stepwise and grouped forward stepwise model selection

### 2013-09-24 paper/paper.tex
Editing paper

% "Title of the paper"
\title{Significance testing and forward stepwise with the group lasso}

@@

Forward stepwise regression is a stochastic model selection procedure
that begins with an empty model and adds the best predictor variable
in each step.  Classical significance tests fail when a model has been
selected this way and tend to be anti-conservative.  Recently,
\cite{significance:lasso} found a novel test statistic with an
appropriate null distribution that behaves well when a model has been
selected using the lasso \citep{tibshirani:lasso}.
\cite{tests:adaptive} modified and extended those results to the
group lasso \citep{grouplasso} and other adaptive regression
problems.  The present work
explores the behavior of those test statistics for models selected by
forward stepwise procedures and works out some of the details
involved in applying these methods to models with grouped variables.
We find that our test statistics can be used for valid significance
testing, or for tempering the aggressive nature of forward stepwise
model selection.  The resulting methods may be less computationally
intensive than choosing a regularization parameter for the group lasso
by cross-validation.

@@

@@

@@

\emph{(For this section I have a lot of stuff written that can just be pasted in once I'm done wrangling the KKT conditions for the unequal weight case)}

@@

@@

\item \todo Add the figures to this section
\item \todo Convert to exposition instead of bulleted list
  \item As in LTTT, $T = \lambda_1 (\lambda_1 - M)$ and $M = \lambda_2$
  \item Convergence to the limiting Exp(1) distribution is too slow
    \[
      \frac{P(\chi_k / w_g \geq m + t/m)}{P(\chi_k / w_g \geq m)} \to e^{-t} \text{ as } m \to \infty
    \]
    (when the group achieving $\lambda_1$ is group $g$ and has rank $k$)
  \item The limiting distribution only depends on $T$, but we also observe $M$
  \item Let's just try the ratio (conditional $\chi_k$ tail probability) evaluated at $T$ and $M$ (it works better)
  \item Going one step further, instead of using the approximation (see LTTT Proof of Lemma 5)
    \[
      \frac{M + \sqrt{M^2+4t}}{2} \approx M + \frac{t}{M}
    \]
    we can just use the left hand side
  \item For $T = \lambda_1(\lambda_1 - M)$ the left hand side simplifies to $\lambda_1$
  \item Now our p-value is
    \[
      \frac{P(\chi_k / w_g \geq \lambda_1)}{P(\chi_k / w_g \geq \lambda_2)}
    \]   
\end{itemize}

\subsection{Can we do $\lambda_k$? Don't know yet}

\section{Forward stepwise procedures}
\todo This is potentially the second largest thing not done yet. However, if it turns out we can't think of a better stopping rule, then this section is done and just needs to be written (and would not take long).

\section{Simulations }
(I've done many of these and have a lot of code, so I can produce a lot of output for this section)
\todo Modify some of my previous simulations after deciding on a stopping rule, decide which simulations to put here.

\section{Real data example}
\todo This is definitely the single largest part I have not done yet.

>>>>

% "Title of the paper"
\title{Significance testing with forward stepwise and grouped forward
  stepwise model selection}

@@

Forward stepwise regression is a stochastic model selection procedure
that begins with an empty model and adds the best predictor variable
in each step.  Classical significance tests fail when a model has been
selected this way and tend to be anti-conservative.  Recently,
\cite{significance:lasso} found a novel test statistic with an
appropriate null distribution that behaves well when a model has been
selected using the lasso \citep{tibshirani:lasso}.
\cite{tests:adaptive} modified and extended those results to the
group lasso \citep{grouplasso} and other adaptive regression
problems.  The present work explores the behavior of those test
statistics for models selected by forward stepwise procedures and
works out some of the detailsinvolved in applying these methods to
models with grouped variables. We find that our test statistics can be
used for valid significance testing, or for tempering the aggressive
nature of forward stepwise model selection.  The resulting methods may
be less computationally intensive than choosing a regularization
parameter for the (group) lasso by cross-validation.

\todo Write about more differences/advantages of this paper- maybe not
in this section, but: using non-asymptotic p-values, forward step is
simple(r than lasso), more?

@@

\todo Fix references below

@@

\todo Update this section to match/complement \citep{tests:adaptive}

@@

\todo Modify write-up to match notation with \cite{tests:adaptive} and
then paste it in here

@@

Maybe just reference \cite{tests:adaptive}? It might be worthwhile to
leave in the connection with \cite{significance:lasso} (getting our
test statistic by not using the approximation)

@@

\item \todo Add the figures to this section
\item \todo Convert to exposition instead of bulleted list
\item \todo Update to reflect latest work
  \item As in LTTT, $T = \lambda_1 (\lambda_1 - M)$ and $M = \lambda_2$
  \item Convergence to the limiting Exp(1) distribution is too slow
    \[
      \frac{P(\chi_k / w_g \geq m + t/m)}{P(\chi_k / w_g \geq m)} \to e^{-t} \text{ as } m \to \infty
    \]
    (when the group achieving $\lambda_1$ is group $g$ and has rank $k$)
  \item The limiting distribution only depends on $T$, but we also observe $M$
  \item Let's just try the ratio (conditional $\chi_k$ tail probability) evaluated at $T$ and $M$ (it works better)
  \item Going one step further, instead of using the approximation (see LTTT Proof of Lemma 5)
    \[
      \frac{M + \sqrt{M^2+4t}}{2} \approx M + \frac{t}{M}
    \]
    we can just use the left hand side
  \item For $T = \lambda_1(\lambda_1 - M)$ the left hand side simplifies to $\lambda_1$
  \item Now our p-value is
    \[
      \frac{P(\chi_k / w_g \geq \lambda_1)}{P(\chi_k / w_g \geq \lambda_2)}
    \]   
\end{itemize}

\section{Forward stepwise procedures}

\todo Expand this section

\begin{itemize}
  \item Brief background, cite some original papers
  \item Describe exactly how we do each step (projection, residuals, etc) 
  \item Stopping rules, cite new paper on lasso, perhaps we have
    a computation advantage
\end{itemize}

\section{Simulations}

\todo Expand, include simulation results (copy latex for
includegraphics etc), do the simulation comparing stopping rules

\begin{itemize}
  \item Show null and non-null p-value-by-step plots for several examples
  \item Discuss one of these carefully (perhaps with a noise variable
    entering before a signal variable), for several fixed stopping points
  \item Compare a few stopping rules, e.g. naive one(s),
    TailStop/HybridStop, AIC/BIC/Cp
  \item (the stopping comparisons are not done yet, but I am guessing
    they will be comparable, perhaps AIC/BIC/Cp will be better, and in
    that case look for other advantages of ours to mention,
    e.g. interpretability for being based on p-values rather than a
    complexity penalty)

\section{Real data example}
\todo Simulation with non-Gaussian design matrix (from AIDS data probably)

\section{Discussion}

\todo After finising everything else, move some points of discussion
here, re-read and see if there's anything else interesting to comment
on here. Mention ongoing work
